BlogForever Crawler: Techniques and Algorithms to Harvest Modern Weblogs

### 2013-11-14 tex/3-algorithms.tex
Add footnote.
Complete techiques head paragraph with a sentence on scalability.

This section explains in details the content wrapper generation algorithm and it's variations for authors, date and comments. We will see how our seemingly brute force approach can be tweaked in order to achieve reasonable running times.

\subsection{Assumptions}
Being a subset of XML, (HTML)* (HTML) documents are often categorized as semi-structured*. Some sementic tags were recently introduced in HTML*footnote* language specification, bringing **. If properly used, tags such as `<article>`, `<title>` and `<date>` can greatly simlify the tasks of content identification and extraction. However, the practice shows that these recent convetions are use by very few websites. Most are still using the more traditional aproach where pages are arbitrery hierarchi of `<div>` tags with arbitrery `class` or `id` names.

Working with blogs allows to make assumptions that are central in our extraction procedure:
1. Web feeds provide structured and standardised view of the last posts
2. Posts of a same blog share the same HTMP structure.

@@

\subsection{Content extraction}
- definitions, args and return value \\
- related algos, generale brute force vue \\
- algorithm \\
- selectors (id, else class) \\
- string similarity \\

\subsection{Variations for comments and date}
All the details about how to use the same algorithm to extract comments and dates.

>>>>

This section explains in details the algorithm we developed to extract blog posts content and it's variations for authors, date and comments.
webfeeeeeeeeds
We will see how our seemingly brute force approach can be tweaked in order to achieve reasonable running times.

\subsection{Assumptions}

\cite{worldwidewebconsortiumw3c2002}
If properly used, tags such as `<article>`, `<title>` and `<date>` can greatly simplify the tasks of content identification and extraction. However, practice shows that these recent conventions are use by very few websites.

Most are still using the more traditional approach where pages are arbitrary hierarchy of `<div>` tags with arbitrary `class` or `id` names.

Working with blogs allows to make assumptions that are central in our extraction procedure:
1. Web feeds provide structured and standardised view of the last posts
2. Posts of a same blog share the same HTMP structure.
\footnote{We constated in the evaluation that all blogs where our system failed to extract content violated one of these assumptions.}

@@

\subsection{Content extraction}
- definitions, args and return value \\

\subsection{Variations for comments and date}

\subsection{Motivation}
- getting content from html is not easy. \cite{w3c2002}
- assumptions when working with blogs
- web feeds limitations
- input output

\subsection{Content extraction}
- related algos, generale brute force vue
- algorithm
- xpath selectors (id, else class, else path)
- string similarity
- caching

\subsection{Variations for comments, date and authors extraction}
- comments
- date authors

### 2013-11-14 tex/4-techniques.tex
Complete techiques head paragraph with a sentence on scalability.

This section gives an overview of different techniques used in our crawler. We first show how we integrated a headless web browser into the harvesting process to support blogs that use JavaScript to display page content. The overall software architecture with then be discussed, introducing the Scrapy framework and the different addition we implemented for our use case.

\subsection{JavaScript rendering}
% Introduction
JavaScript is a widely used use language for client-side web scripting. While some applications simply use it for aesthetics aspects such as menus and animations, an increasing number of websites use JavaScript to download and display content. In such circumstances, traditional HTML based crawled would not see the web site as it would be presented to a human visitor and might therefore be obsolete for extracting data from the page.

@@

% \subsection{Architecture}
% \subsubsection{Item pipeline}
% - item pipeline, modularity \\

\subsection{Architecture}

@@

\subsection{Enriching Scrapy}
In order to find and identify blog posts, our implementation enriches Scrapy with two components to narrow the extraction process to the subsets of blog pages holding blog posts: blog-post identification and download priority heuristic. Given an entry point to a website, the default Scrapy behavior allows to look over all pages of the same domain in a \emph{last in first out} manner. The \emph{blog-post identification} function is able to identify from a URL whether or not the corresponding page is a blog-post. Internally, this function uses a regular expression constructed for each blog from it's web feed entries. These constitute the only set of known blog post URLs, and can therefore be used identify the structure of blog post URLs. This simple approach requires that blogs use the same pattern for all posts (or false negative will occur) which has to be distinct for non post pages (or false positive will occur). In practice this assumption held for all blog platforms we encountered during the developments and seems to be a common practice among web developer.

@@

\subsection{Scalability}
When aiming to work with a large number of inputs, it is crucial that every layer of the system is build to be scalable. Citing the Reactive Manifesto\cite{thereactivemanifesto2013}:

>>>>

This section gives an overview of different techniques used in our crawler. We first show how we integrated a headless web browser into the harvesting process to support blogs that use JavaScript to display page content. The overall software architecture with then be discussed, introducing the Scrapy framework and the enrichments we implemented for our specific use case. The section will conclude with a discussion about how the crawler design leads nicely into a scalable and fault resilient distributed architecture.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{JavaScript rendering}
% Introduction
JavaScript is a widely used use language for client-side web scripting. While some applications simply use it for aesthetics aspects such as menus and animations, an increasing number of websites use JavaScript to download and display content. In such circumstances, traditional HTML based crawled would not see the web site as it would be presented to a human visitor and might therefore be obsolete for extracting data from the page.

@@

%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Architecture}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Enriching Scrapy}
In order to find and identify blog posts, our implementation enriches Scrapy with two components to narrow the extraction process to the subsets of blog pages holding blog posts: blog-post identification and download priority heuristic. Given an entry point to a website, the default Scrapy behavior allows to look over all pages of the same domain in a \emph{last in first out} manner. The \emph{blog-post identification} function is able to identify from a URL whether or not the corresponding page is a blog-post. Internally, this function uses a regular expression constructed for each blog from it's web feed entries. These constitute the only set of known blog post URLs, and can therefore be used identify the structure of blog post URLs. This simple approach requires that blogs use the same pattern for all posts (or false negative will occur) which has to be distinct for non post pages (or false positive will occur). In practice this assumption held for all blog platforms we encountered during the developments and seems to be a common practice among web developer.

@@

%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Scalability}
When aiming to work with a large number of inputs, it is crucial that every layer of the system is build to be scalable. Citing the Reactive Manifesto\cite{thereactivemanifesto2013}:
